\chapter*{\hfill Acknowledgement \hfill}
\addcontentsline{toc}{chapter}{Acknowledgement}
\addcontentsline{toe}{chapter}{Acknowledgement}

Studying for a PhD and moving to a foreign country has certainly been a valuable, exciting and an enriching experience, both personally and professionally, but it has been very challenging as well. I could not have succeeded without the advice, support and influence of many colleagues, friends and family. My thanks are due first and foremost to my advisor Prof. Feng Xia, for being a consistent source of support and encouragement. He always provides me with great insight and useful advice whenever I need discussion. His motivation and drive for excellence set an excellent example for my PhD study and his guidance and help have made my Ph.D. program a challenging and productive one. His professional dedication and integrity with positive attitude will always been an inspiration to me. I will be forever grateful for his help. I will also like to thank Dr. Xiangjie Kong for all his help and assistance as a co-advisor.

During the whole period of my doctorate study, I have been immensely fortunate to work and co-author with many great individuals, notably, Prof. Laurence Yang, Prof. Jianhua Ma, Prof. Joel Rodrigues, Prof. Zhikui Chen, Prof. Zhongxuan Luo, Dr. Tie Qiu, Prof. Runhe Huang and Dr. Saeid Abolfazli. I am deeply indebted to members of DUT Phone Lab. I have received continuous help from Nana, Hannan, Dimitry, Behrouz, Jack, Wei Wang, Qiuyuan Yang, Haifeng Liu, Zhen Chen, Liu Li, Jing Li, Rina, Aziz and others in both academic and social sides. They made the time I spent working towards my Ph.D. full of excitement. I thank everyone for their kindness and help. I am grateful to Yancy Davis for his help on proofreading some of my works, Hayat Dino and Teshome Megersa for their help in proofreading this dissertation. I thank all of my PhD dissertation committee members and reviewers for their valuable comments and feedback. I cannot forget my friends and country-mates at Dalian and Chongqing who were always supportive of me.

Finally, I am grateful for my parents, Mohammed Ahmed and Lubaba Gizaw, and my brother Anewar. They gave me the strength to fight for my goals and ambitions, and provided me with indispensable support that was essential during the course of my study, and for the completion of this dissertation.


\vspace{1cm}
\hfill  Ahmedin~~~~~

\hspace{1cm}
\hfill November 2014~~~
