\chapter*{\hfill Published Academic Theses during PhD Period \hfill}
\addcontentsline{toc}{chapter}{Published Academic Theses during PhD Period}
\addcontentsline{toe}{chapter}{Published Academic Theses during PhD Period}

\renewcommand{\labelenumi}{[\arabic{enumi}]}
\section*{Journal Papers}
\begin{enumerate}
\item
Feng Xia, \textbf{Ahmedin Mohammed Ahmed}, Laurence Tianruo Yang, Zhongxuan Luo. Community-based Event Dissemination with Optimal Load Balancing, IEEE Transactions on Computers, 2014, DOI: 10.1109/TC.2014.2345409. (Served as Chapter 5 of this dissertation)

\item
\textbf{Ahmedin Mohammed Ahmed}, Tie Qiu, Feng Xia, Behrouz Jedari, Saeid Abolfazli. Event-based Mobile Social Networks: Services, Technologies and Applications, IEEE Access, vol. 2, no. 500-513, 2014. (Served as Chapter 2 of this dissertation)

\item
Feng Xia, \textbf{Ahmedin Mohammed Ahmed}, Laurence Tianruo Yang, Jianhua Ma, Joel Rodrigues. Exploiting Social Relationship to Enable Efficient Replica Allocation in Ad-hoc Social Networks, IEEE Transactions on Parallel and Distributed Systems, vol. 25, no. 12, pp. 3167-3176, 2014. (Served as Chapter 4 of this dissertation)

\item
Hannan Bin Liaqat, Feng Xia, Qiuyuan Yang, Zhenzhen Xu, \textbf{Ahmedin Mohammed Ahmed}, Azizur Rahim. Bio-inspired Packet Dropping in Socially-aware Ad-hoc Networks, International Journal of Communication Systems, 2014, DOI: 10.1002/dac.2857.

\item
Feng Xia, Li Liu, Jie Li, \textbf{Ahmedin Mohammed Ahmed}, Laurence Tianruo Yang, Jianhua Ma. BEEINFO: Interest-based Forwarding Using Artificial Bee Colony for Socially-aware Networking, IEEE Transactions on Vehicular Technology, 2014, DOI: 10.1109/TVT.2014.2305192.

\item
Li Liu, Qiuyuan Yang, Xiangjie Kong, Hannan Bin Liaqat, \textbf{Ahmedin Mohammed Ahmed}, Nakema Deonauth, Feng Xia. Com-BIS: A Community-based Barter Incentive Scheme in Socially Aware Networking, International Journal of Distributed Sensor Networks, Accepted for Publication, 2014.

\item
Hannan Bin Liaqat, Feng Xia, Jianhua Ma, Laurence Tianruo Yang, \textbf{Ahmedin Mohammed Ahmed}, Nana Yaw Asabere. Social Similarity-aware TCP with Collision Avoidance in Ad-hoc Social Networks, IEEE Systems Journal, 2014, DOI: 10.1109/JSYST.2014.2305191.

\item
Feng Xia, Nana Yaw Asabere, \textbf{Ahmedin Mohammed Ahmed}, Jing Li and Xiangjie Kong. Mobile Multimedia Recommendation in Smart Communities: A Survey, IEEE Access, vol.1, pp.606-624, 2013.

\end{enumerate}

\section*{Conference Papers}
\begin{enumerate}
\item
\textbf{Ahmedin Mohammed Ahmed}, Feng Xia, Qiuyuan Yang, Hannan Bin Liaqat, Zhikui Chen, Tie Qiu. Bacteria Inspired Mitigation of Selfish Users in Ad-hoc Social Networks, The 15th ACM International Symposium on Mobile Ad Hoc Networking and Computing (MobiHoc), Philadelphia, PA, USA, August 11-14, 2014. (Served as Chapter 6 of this dissertation)

\item
\textbf{Ahmedin Mohammed Ahmed}, Qiuyuan Yang, Nana Yaw Asabere, Tie Qiu, Feng Xia. ComPAS: Maximizing Data Availability With Replication in Ad-hoc Social Networks, The 23rd International World Wide Web Conference (WWW), Poster Track, Seoul, Korea, April 7-11, 2014. (Served as Chapter 4 of this dissertation)

\item
\textbf{Ahmedin Mohammed Ahmed}, Feng Xia, Nana Yaw Asabere, Hannan Bin Liaqat, Jie Li. Social Community-Partition Aware Replica Allocation in Ad-hoc Social Networks, in Proceedings of IEEE International Conference on Cyber, Physical and Social Computing (IEEE CPSCom), pp. 834-841, Beijing, China, Aug 21-23, 2013. (Served as Chapter 4 of this dissertation)

\item
Hannan Bin Liaqat, Qiuyuan Yang, \textbf{Ahmedin Mohammed Ahmed}, Zhenzhen Xu, Tie Qiu, Feng Xia. A Social Popularity Aware Scheduling Algorithm for Ad-hoc Social Networks, The 11th International Joint Conference on Computer Sciences and Software Engineering (JCSSE), Pattay City, Thailand, May 14-16, 2014.
\end{enumerate}

\section*{Book Chapter}
\begin{enumerate}
\item
Behrouz Jedari, Feng Xia, \textbf{Ahmedin Mohammed Ahmed}, Poria Pirozmand, and Yashar Najaflou. Chapter 11: Using Social Network Analysis (SNA) to Design Socially Aware Network Solutions in Delay-tolerant Networks (DTNs), in: Advances in delay-tolerant networks (DTNs), edited by J.J.P.C Rodrigues, Woodhead Publishing Series in Electronic and Optical Materials: Number 67, 2014, DOI: 10.1533/9780857098467.2.200.
\end{enumerate}

\section*{Papers Under Review}
\begin{enumerate}

\item
\textbf{Ahmedin Mohammed Ahmed}, Feng Xia, Runhe~Huang, Jianhua Ma. Middleware for Ad-hoc Social Networks: Design Challenges, IEEE Communications Magazine. (Served as Chapter 3 of this dissertation)(Second round review after Major Revision)

%\item
%\textbf{Ahmedin Mohammed Ahmed}, Feng Xia, Jun Zhang, Saeid Abolfazli, Zohreh Sanaei. BoDMaS: Bio-inspired Detection and Mitigation of Node Selfishness in Ad-hoc Social Networks, IEEE Transactions on Human Machine Systems. (Served as Chapter 6 of this dissertation)

\item
Behrouz Jedari, Feng Xia, \textbf{Ahmedin Mohammed Ahmed}, Jun Zhang. A Survey on Routing and Data Dissemination in Opportunistic Mobile Social Networks, Journal of Network and Computer Applications.

%\item
%Feng Xia, Jie Li, Qiuyuan Yang, Jiannong Cao, Li Liu, \textbf{Ahmedin Mohammed Ahmed}. Data Dissemination Using Interest Tree in Socially Aware Networking, IEEE Transactions on Parallel and Distributed Systems.

\item
Jie Li, Feng Xia, Li Liu, \textbf{Ahmedin Mohammed Ahmed}, Hannan Bin Liaqat, Zhenzhen Xu. Geo-Social Distance Based Data Dissemination for Socially Aware Networking, IET Networks.

\item
Hannan Bin Liaqat, Feng Xia, \textbf{Ahmedin Mohammed Ahmed}, Li Liu, Zhenzhen Xu, Xiangjie Kong. User Popularity-based Packet Scheduling for Congestion Control in Ad-hoc Social Networks, Journal of Computer and System Sciences.

\end{enumerate}



